---
title: "Play with Quarto v. 1.4"
date: last-modified
author: Charalampos A. Lazaris
toc: true
toc-depth: 2
format: 
    html:
        theme: cerulean
        embed-resources: true
        fontsize: 1.5em
code-line-numbers: true
code-overflow: scroll
code-fold: show
highlight-style: tango
keywords: ["Quarto", "tutorial", "R"]
---

# Introduction

This is a Quarto tutorial based on the official Posit cheatsheet. It features some of the new features in Quarto v. 1.4. 

# Code

Let's insert some inline code in R: `{r} p <- 1 + 1` gives `{r} p`

Here is some `R` code:

```{r}
p <- 1 + 1
print(p)
```

Now, let's import some data and create a graph, after loading the required libraries:

```{r}
#| warning: false # Do not display warnings
library(tidyverse)
```

```{r}
data(iris)
glimpse(iris)
```

We now plot `Petal.Length` vs. `Petal.Width`:

```{r}
#| fig-align: center
#| fig-height: 6
#| fig-width: 8
ggplot(data = iris, aes(x = Petal.Width, y = Petal.Length)) +
    geom_point() +
    geom_smooth(method = "lm", se = TRUE) +
    ggtitle("Petal length vs. petal width") +
    xlab("Petal width") + ylab("Petal length") +
    theme_bw()
```

::: {.callout-tip title="Consistency" collapse="true"}
Use `dplyr` for data wrangling and `ggplot2` for plotting - keep it consistent
:::